Dissertation Manuscript

### 2023-10-19 paper.qmd
add docx and md download options

  <a class="btn btn-danger btn-sm mb-1" href="/Manuscript/output/TG_Full_Dissertation.pdf" target="manuscript">
  <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;PDF
  </a>

@@

>>>>

  <a class="btn btn-warning btn-sm mb-1" href="/Manuscript/output/TG_Full_Dissertation.pdf" target="manuscript">
  <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;PDF
  </a>

@@

    <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/output/TG_Full_Dissertation.docx">
  <iconify-icon inline="" icon="fa6-solid:file-word"></iconify-icon> &ensp;DOCX <small>(download)</small>
  </a>

  <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/manuscript.html.md">
  <iconify-icon inline="" icon="fa6-solid:file-word"></iconify-icon> &ensp;md <small>(download)</small>
  </a>
